\chapter*{Acknowledgements}
\vspace{1cm}

I would like to thank all people that supported me in many very different ways during my PhD.
I want to thank Christian Sander and Peter Schleper who agreed on reviewing my dissertation 
and the other members of the committee, Isabell Melzer-Pellmann, Jan Louis and Dieter Horns who made a very uncomplicated and rapid planning of my disputation possible.
I want to thank Johanner Haller to step in spontaneously as a referee for my disputation.

This work has only been possible due to the continous support by Christian Sander, Lukas Vanelderen, Hartmut Stadie, Lo\"{i}c Quertenmont, Wells Wulsin und Francesco Pandolfi.
Interesting and helpful exchanges and discussions with them facilitated my work, and gave me a lot of pleasure during the last years. 

I would like to thank all my colleagues in Hamburg, since they enabled working in a very nice and relaxed atmosphere. 
Hereby, I would like to thank especially Mareike Meyer, Kristin Goebel und Rebekka H\"{o}ing, my colleagues with whom I shared the office most of time during the last years. 
Thank you for the support during and apart of work.

Finally, I would like to say thank you to all those who made me not loosing fully my psychologically and physical stability: my friends, my family, and especially Markus.




%FIXME
%Zu guter Letzt möchte ich mich bei allen bedanken, die das Gelingen dieser Arbeit ermöglicht haben.
%Ich bedanke mich bei Chrstian Sander und Peter Schleper, die sich bereit erklärt haben, meine Dissertation zu begutachten und bei den  weiteren Mitgliedern der Prüfungskommission, Dieter Horns, Isabell Melzer-Pellmann und Jan Louis, die mir eine sehr unkomplizierte und schnelle Planung der Dissertation ermöglicht haben.

%Diese Arbeit war nur möglich durch die stetige fachliche Unterstützung durch Christian Sander, Lukas Vanelderen, Hartmut Stadie, Lo\"{i}c Quertenmont, Wells Wulsin und Francesco Pandolfi.
%Der stetige Austausch und die Unterstützung haben mir meine Arbeit sehr erleichtert und mir immer viel Freude bereitet.
%Dadurch dass die Türen von jenen stets geöffnet waren und einen intensiven Austausch über meine Arbeit ermöglicht haben, wurde meine Arbeit sehr erleichtert. 

%Meinen Kollegen in Hamburg will ich danken, da durch sie ein Arbeiten in sehr entspannter Atmosphäre möglich wurde.
%Dabei will ich natürlich ganz besonders Mareike Meyer, Kristin Goebel und Rebekka Höing danken, meinen Kolleginnen mit denen ich die meiste Zeit während der letzten Jahren ein Büro geteilt habe und mit denen ich bei und jenseits der Arbiet viel Freude und Spaß hatte.    

%Abschließend, will ich mich bei jenen bedanken, durch die ich mein psychisches und physisches Gleichgewicht nie vollständig verloren habe: meinen Freunden, meiner Familie und ganz besonders Markus.  
